Global case

### 2025-05-20 lipschitz 2025/Lipitschz.tex
update

%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
%	
	\subsection{Improving the Accuracy of the Simplified Model}
	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed. (This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)

@@

	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
	the accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with $\hat{x}'_i=\ReLU(x'_i)$) are the follows:
	\begin{align*}
		& \begin{aligned}
			y_i + x'_i &\leq a\beta_i        &\quad\quad
			y_i + x'_i &\geq (1-a)\alpha_i \\
			x'_i       &\leq a'\beta_i       & 
			x'_i       &\geq (1-a')\alpha_i \\
			\hat{y}_i  &\leq a\gamma_i       &
			\hat{y}_i  &\geq -a'\gamma_i \\
			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
			\hat{y}_i  &\leq -x'_i + a\beta_i &
			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
		\end{aligned}
	\end{align*} Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$. The constraints for $x_i$s are not necessary, or at least their MILP constraints can be relaxed to LP without reducing accuracy.

>>>>

%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
%	
	\subsection{Improving the Accuracy of the Simplified Model}
	We can improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.

%	(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)

@@

	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
	\begin{align*}
		& \begin{aligned}
			y_i + x'_i &\leq a\beta_i        &\quad\quad
			y_i + x'_i &\geq (1-a)\alpha_i \\
			x'_i       &\leq a'\beta_i       & 
			x'_i       &\geq (1-a')\alpha_i \\
			\hat{y}_i  &\leq a\gamma_i       &
			\hat{y}_i  &\geq -a'\gamma_i \\
			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
			\hat{y}_i  &\leq -x'_i + a\beta_i &
			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
		\end{aligned}
	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.

	Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
